\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2024-01-23 manuscript_BiSC_outdoor_AP.tex
Updates from Overleaf

The performance of the models varied substantially across different pollutants as shown in the metrics displayed in the \Cref{fig3}, albeit all models showed moderate to good performance. HM outperformed LUR and DM models in predicting  NO\textsubscript{2} (R\textsubscript{2} = 0.64), PM\textsubscript{2.5} (R\textsubscript{2} = 0.66), BC (R\textsubscript{2} = 0.86) with corresponding RMSE values 7.48 \mu\)g/m\textsuperscript{3}, 3.45 \mu\)g/m\textsuperscript{3} and 0.23 \mu\)g/m\textsuperscript{3} respectively. LUR models show better performance for traffic-related air pollutants tracers PM\textsubscript{2.5 - Fe} (R\textsuperscript{2} = ), PM\textsubscript{2.5 - Cu} (R\textsuperscript{2} = ), and PM\textsubscript{2.5 - Zn} (R\textsuperscript{2} = ) compared to HM.

@@

\newpage
\subsection{Comparison between models} % broad title then change this
% --- Exposure concentrations --- %
Predictions from outdoor air pollution concentration exposure during the entire pregnancy for each pollutant and model is shown in \Cref{fig2}. The exposure range was larger for the LUR model for all the pollutants assessed. Dispersion model predicted lower exposure concentration values than LUR and Hybrid. In addition to that HM show less variability in the exposure concentration.

>>>>

The performance of the models varied substantially across different pollutants as shown in \Cref{fig3}. All models exhibit relatively good performance, evaluated by the following metrics; $R^{2}_{\text{10-CV}}$, $RMSE_{\text{10-CV}}$, $R^{2}_{\text{LOOCV}}$, and $RMSE_{\text{LOOCV}}$. The HM performance for NO\textsubscript{2} ($R^{2}_{\text{10-CV}} = 0.64$), PM\textsubscript{2.5} ($R^{2}_{\text{10-CV}} = 0.66$), and BC ($R^{2}_{\text{10-CV}} = 0.86$) was moderate to good, with corresponding $RMSE_{\text{10-CV}}$ values of $7.48 \, \mu\text{g/m}^{3}$, $3.45 \, \mu\text{g/m}^{3}$, and $0.23 \, \mu\text{g/m}^{3}$ while for PM\textsubscript{2.5} componentes, the performance was more conservative with PM\textsubscript{2.5 - Fe} ($R^{2}_{\text{10-CV}} = 0.89$), PM\textsubscript{2.5 - Cu} ($R^{2}_{\text{10-CV}} = 0.87$), and PM\textsubscript{2.5 - Zn} ($R^{2}_{\text{10-CV}} = 0.85$). Conversely, LUR models showed better performance in predicting PM\textsubscript{2.5 - Fe} ($R^{2}_{\text{LOOCV}} = 0.89$), PM\textsubscript{2.5 - Cu} ($R^{2}_{\text{LOOCV}} = 0.87$), and PM\textsubscript{2.5 - Zn} ($R^{2}_{\text{LOOCV}} = 0.85$) concentration levels in comparison to  NO\textsubscript{2} ($R^{2}_{\text{LOOCV}} = 0.62$), PM\textsubscript{2.5} ($R^{2}_{\text{LOOCV}} = 0.45$), and BC ($R^{2}_{\text{LOOCV}} = 0.83$).

@@

\newpage
\subsection{Comparison between models} % broad title then change this
% --- Exposure concentrations --- %
Predictions from outdoor air pollution concentrations exposure during the entire pregnancy for each pollutant and model is shown in \Cref{fig2}. The exposure range was larger for the LUR model for all the pollutants assessed. Dispersion model predicted lower exposure concentration values than LUR and Hybrid. In addition to that HM show less variability in the exposure concentration.
